### 2012-10-03 4.tex
Edits to 2 and 4, and writing in 3

\paragraph{Affricates} If the affricates [tʃ, dʒ] are treated as stop-fricative sequences \citep[e.g.,][]{Hualde1988,Lombardi1990}, the previous principle will incorrectly assign the two segments of the affricate to separate syllables before stressed lax vowels (e.g., *\emph{ra}[t.ʃ]\emph{et} or \emph{a}[d.ʒ]\emph{ile}) unless some ad hoc constraint \citep[e.g.,][]{Wells1990} is in place. A more traditional analysis of affricates, in which they are simple segments distinguished from pure stops by stridency \citep[24]{Jakobson1961} or delayed release (\emph{SPE}:321f.) is assumed here, following \citeauthor{Pierrehumbert1994}. This assumption can be motivated by the tendency of affricates to pattern with individual segments in phonotactic generalizations. For instance, Classical Nahua allows the affricate series [ts, tʃ, tɬ] in onsets, but bans all other onset clusters \citep[9]{Launey2011}. 
%\citet[86]{Butskhrikidze2002} notes a similar generalization in the consonant clusters of Georgian.

@@

\paragraph{[j] onglides} While some have argued that the front onglide in words such as \emph{val}[j]\emph{ue} is inserted by rule (\emph{SPE}:196, \citealp[][89]{Halle1985a}, \citealp[][217]{McMahon1990}), the very presence or absence of the glide is contrastive (e.g., \emph{coo}/\emph{coup} \alt{} \emph{queue}, \emph{booty} \alt{} \emph{beauty}) indicating that it is present in underlying representation (\citealp{Anderson1988b}, \citealp[278]{Borowsky1986}). The front onglide is further assumed to be assigned to the nucleus, except when the onset would otherwise be null (e.g., \emph{jun}[j]\emph{or}). There is considerable evidence for this assumption. When [j] is a simplex onset, it may be followed by any vowel \citep[][276]{Borowsky1986}, but when [j] is immediately preceded by an onset consonant (e.g., [bj]\emph{ugle}), the following vowel is always [u], suggesting that the glide is nuclear (\citealp{Davis1995}, \citealp[][61f.]{Harris1994}, \citealp[][232]{Hayes1980}). \citet[][42]{Clements1983} note that /m, v/ do not appear in onset clusters, though they may be followed by [ju] in words like [mj]\emph{use} or [vj]\emph{iew}, also suggesting the nuclear affiliation of the glide. There is also external support for this analysis: the [ju] in words like \emph{spew} may pattern together in Pig Latin \citep{Davis1995,Idsardi2005}, \emph{shm}-reduplication \citep{Nevins2003}, and speech errors (e.g., [kju]\emph{mor} [h]\emph{omponent}, intended [hju]\emph{mor component}; \citealp[130]{Shattuck-Hufnagel1986}).

@@

\paragraph{Post-vocalic \emph{r}} Word-medial post-vocalic \emph{r} has been lost in Received Pronunciation, the standard accent of the CELEX transcriptions. Even in \emph{r}-ful dialects, though, there is reason to believe that post-vocalic \emph{r} is fact nuclear, and thus irrelevant to syllable contact clusters. Many vowel contrasts are suspended before \emph{r} (e.g., \citealt[269f.]{Fudge1969}, \citealt[][255]{Harris1994}): compare American English \emph{fern}, \emph{fir}, \emph{fur} to \emph{pet}, \emph{pit}, \emph{putt}. Post-vocalic \emph{r} patterns with vowels and not other consonants for several phonological processes: it is the only consonant which does not block variable glottalization of following /t/ in British dialects \citep[258]{Harris1994}.

@@

\noindent Post-vocalic \emph{r} is the only consonant which does not trigger variable deletion of a following /t, d/ in American dialects \citep[8]{Guy1980}.

@@

\begin{example}[\textsc{Obstruent Voice Assimilation}]
\xymatrix@R=24pt@C=24pt{
\txt{[α \textsc{Voice}]}\ar@{-}[d]\ar@{--}[dr] &                               \\
\txt{C}\ar@{-}[d]                              & \txt{C}\ar@{-}[d]             \\
\txt{[$+$\textsc{Obstruent}]}                  & \txt{[$+$\textsc{Obstruent}]} \\
}
\end{example}

@@

A final alternation targeting English syllable contact clusters is the simplification of geminates derived by certain affixes. For instance, the deadjectival adverbial suffix \emph{-ly} rarely produces a geminate when it attaches to /l/-final roots (e.g., \emph{norma}[l]\emph{y}, cf. \emph{calm}[l]\emph{y}). Degemination is also found in /d/-final roots selecting the irregular /-t/ past tense suffixes (e.g., \emph{bend}/\emph{ben}[t], \emph{build}/\emph{buil}[t]). More complicated cases of \textsc{Degemination} can be found in Latinate prefix allomorphy (\emph{SPE}:148; \citealp[102]{Borowsky1986}). Identical adjacent consonants do not occur in the corpus, nor do those which differ only in voice, such as *[p.b], which would be made identical by the operation of \textsc{Obstruent Voice Assimilation}. This absence is unlikely to be due to chance.

>>>>

\paragraph{Affricates} If the ffricates [tʃ, dʒ] are treated as stop-fricative sequences \citep[e.g.,][]{Hualde1988,Lombardi1990}, the previous principle will incorrectly assign the two segments of the affricate to separate syllables before stressed lax vowels (e.g., *\emph{ra}[t.ʃ]\emph{et} or \emph{a}[d.ʒ]\emph{ile}) unless some ad hoc constraint \citep[e.g.,][]{Wells1990} is in place. A more traditional analysis of affricates, in which they are simple segments distinguished from pure stops by stridency \citep[24]{Jakobson1961} or delayed release (\emph{SPE}:321f.) is assumed here, following \citeauthor{Pierrehumbert1994}. This assumption can be motivated by the tendency of affricates to pattern with individual segments in phonotactic generalizations. For instance, Classical Nahua allows the affricate series [ts, tʃ, tɬ] in onsets, but bans true onset clusters \citep[9]{Launey2011}.
%\citet[86]{Butskhrikidze2002} notes a similar generalization in the consonant clusters of Georgian.

@@

\paragraph{[j] onglides} While some have argued that the front onglide in words such as \emph{val}[j]\emph{ue} is inserted by rule (\emph{SPE}:196, \citealp[][89]{Halle1985a}, \citealp[][217]{McMahon1990}), the very presence or absence of the glide is contrastive (e.g., \emph{coot} \alt{} \emph{cute}, \emph{booty} \alt{} \emph{beauty}) indicating that it is present in underlying representation (\citealp{Anderson1988b}, \citealp[278]{Borowsky1986}). The front onglide is further assumed to be assigned to the nucleus, except when the onset would otherwise be null (e.g., \emph{ju}[n.j]\emph{or}). There is considerable evidence for this assumption. When [j] is a simplex onset, it may be followed by any vowel \citep[][276]{Borowsky1986}, but when [j] is immediately preceded by an onset consonant (e.g., [bj]\emph{ugle}), the following vowel is always [u], suggesting that the glide is nuclear (\citealp{Davis1995}, \citealp[][61f.]{Harris1994}, \citealp[][232]{Hayes1980}). \citet[][42]{Clements1983} note that /m, v/ do not appear in onset clusters, though they may be followed by [ju] in words like [mj]\emph{use} or [vj]\emph{iew}, also suggesting the nuclear affiliation of the glide. There is also external support for this analysis: the [ju] in words like \emph{spew} may pattern together in Pig Latin \citep{Davis1995,Idsardi2005}, \emph{shm}-reduplication \citep{Nevins2003}, and speech errors (e.g., [kju]\emph{mor} [h]\emph{omponent}, intended [hju]\emph{mor component}; \citealp[130]{Shattuck-Hufnagel1986}).

@@

\paragraph{Syllabic \emph{r}} Word-medial syllabic \emph{r} has been lost in Received Pronunciation, the accent used for the CELEX transcriptions. Even in \emph{r}-ful dialects, though, there is reason to believe that syllabic \emph{r} is fact nuclear, and thus irrelevant to syllable contact clusters. Many vowel contrasts are suspended before \emph{r} (e.g., \citealt[269f.]{Fudge1969}, \citealt[][255]{Harris1994}): compare American English \emph{fern}, \emph{fir}, \emph{fur} to \emph{pet}, \emph{pit}, \emph{putt}. Syllabic \emph{r} patterns with vowels and not other consonants for several phonological processes: it is the only consonant which does not block variable glottalization of following /t/ in British dialects \citep[258]{Harris1994}.

@@

\noindent Syllabic \emph{r} is the only consonant which does not trigger variable deletion of a following /t, d/ in American dialects \citep[8]{Guy1980}.

@@

\begin{example}[\textsc{Obstruent Voice Assimilation}]
\xymatrix@R=24pt@C=24pt{
\txt{[α \textsc{Voice}]}\ar@{-}[d]\ar@{--}[dr] &                               \\
\txt{C}\ar@{-}[d]                              & \txt{C}\ar@{-}[d]             \\
\txt{[$-$\textsc{Sonorant}]}                  & \txt{[$-$\textsc{Sonorant}]} \\
}
\end{example}

@@

A final alternation targeting English syllable contact clusters is the simplification of geminates derived by certain affixes. For instance, the deadjectival adverbial suffix \emph{-ly} rarely produces a geminate when it attaches to /l/-final roots (e.g., \emph{fu}[l]\emph{y}, cf. \emph{free}[l]\emph{y}). Degemination is also found in /d/-final roots selecting the irregular /-t/ past tense suffixes (e.g., \emph{bend}/\emph{ben}[t], \emph{build}/\emph{buil}[t]). More complicated cases of \textsc{Degemination} can be found in Latinate prefix allomorphy (see \emph{SPE}:148 and \citealt[102]{Borowsky1986}). Identical adjacent consonants do not occur in the corpus, nor do obstruent clusters which differ only in voice (e.g., *[p.b]), which would be made identical by the operation of \textsc{Obstruent Voice Assimilation}. As shown by the results of the Fisher test, this absence is unlikely to be due to chance.
